Sperm should evolve to make female meiosis fair.

### 2014-05-31 writeup_and_notes/PLoSBioSubmission/CoverLetter.tex
pointed out that figs where in ms
replaced question mark with dash

The requirement of fertilization for the completion of female meiosis in many animal species presents an opportunity for sperm to interfere with the outcome of female meiosis. We employ population genetic theory to show that sperm that enforce fairness in female meiosis are nearly universally favored. As such, we offer a novel interpretation of the requirement of fertilization for the completion of female meiosis ? this requirement potentially represent a collaboration between mother and sperm in the control of fitness reducing meiotic drivers. The application of theory to a basic and unexplained feature of organismal biology, and the interplay between conflict and co-option by numerous parties involved in fertilization make this paper of broad interest to a wide-range of biologists.
\\

@@

We note that while we submitted this as a `Research article,' we are open to reformatting it as an `Unsolved mystery' if the editorial board feels that is more appropriate. 
\\
\\ 
\begin{flushright}
Sincerely,\\
Yaniv Brandvain \\ \& Graham Coop\\
May 31$^{st}$ 2014
\end{flushright}
\end{document}

>>>>

The requirement of fertilization for the completion of female meiosis in many animal species presents an opportunity for sperm to interfere with the outcome of female meiosis. We employ population genetic theory to show that sperm that enforce fairness in female meiosis are nearly universally favored. As such, we offer a novel interpretation of the requirement of fertilization for the completion of female meiosis -- this requirement potentially represent a collaboration between mother and sperm in the control of fitness reducing meiotic drivers. The application of theory to a basic and unexplained feature of organismal biology, and the interplay between conflict and co-option by numerous parties involved in fertilization make this paper of broad interest to a wide-range of biologists.
\\

@@

We note that while we submitted this as a `Research article,' we are open to reformatting it as an `Unsolved mystery' if the editorial board feels that is more appropriate.  We also note that we have included Figures 1 and 2, as wells as Figures S1, S2 and S3 directly in our uploaded PDF.
\\
\\ 
\begin{flushright}
Sincerely,\\
Yaniv Brandvain \\ \& Graham Coop\\
May 31$^{st}$ 2014
\end{flushright}
\end{document}
